Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Fixed text

For this paper, we have built tooling to (\emph{a}) automate the extraction of
raw type signatures from execution traces, (\emph{b}) infer type signatures from
a set of raw types, and (\emph{c}) validate the inferred signatures by the means
of contracts. This section presents each step of this pipeline (\emph{cf.}
Figure~\ref{fig:pipeline}). The pipeline is run in parallel using GNU
parallel~\cite{tange2011_parallel} on Intel Xeon 6140, 2.30GHz with 72 cores and
256GB of RAM).

>>>>

For this paper, we have built tooling to (\emph{a}) automate the extraction of
raw type signatures from execution traces, (\emph{b}) infer type signatures from
a set of raw types, and (\emph{c}) validate the inferred signatures by the means
of contracts. Figure~\ref{fig:pipeline} shows an overview of this pipeline. This
section gives details of the main steps. The pipeline is run using GNU
parallel~\cite{tange2011_parallel} on Intel Xeon 6140, 2.30GHz with 72 cores and
256GB of RAM.
